NLIZE: a Perturbation-Driven Visual Interrogation Tool for Analyzing and Interpreting Natural Language Inference Models

### 2018-03-24 paper/background.tex
add figure
add simple example

\subsection{Natural Language Inference}
\label{sec:languageInference}
Natural Language Inference~\cite{MacCartney2009} is an important machine understanding task in NLP.
The problem definition is to classify the relationship between a premise sentence and a hypothesis sentence.

\begin{center}
 \begin{tabular}{c | c c c c} 
 \hline
  & sentences & entail & contradict  & neutral \\ [0.5ex] 
 \hline
 premise & Jim ate an apple. &  -  &  -  & - \\ 
 hypothesis & Jim ate fruits. & \checkmark &   &  \\
 hypothesis & Jim ate an banana. &  & \checkmark & \\
 hypothesis & Tom ate an apple &  &  & \checkmark \\
 hypothesis & Jim ate a Fuji apple. &   &  & \checkmark? \\
 \hline
\end{tabular}
\end{center}
\shusen{What is the most standard example to illustrate NLI problem?}
\shusen{high level NLP comments}

>>>>

\subsection{Natural Language Inference}
\label{sec:languageInference}
Natural Language Inference~\cite{DaganRothSammons2013} is an important machine understanding task in NLP.
The problem definition is to classify the relationship between a premise sentence and a hypothesis sentence. A simple example is illustrated in Table.~\ref{table:NLI}.

\begin{table}[htbp]
\label{table:NLI}
\centering
\caption{An illustration of natural language inference.}
 \begin{tabular}{c | c c c c} 
 \hline
  & sentences & entail & contradict  & neutral \\ [0.5ex] 
 \hline
 premise & Jim ate an apple. &  -  &  -  & - \\ 
 hypothesis & Jim ate a Fuji apple. &   &  & \checkmark \\
 hypothesis & Jim ate fruits. & \checkmark &   &  \\
 hypothesis & Jim ate an banana. &  & \checkmark & \\
 hypothesis & Tom ate an apple &  &  & \checkmark \\
 %\hline
 %premise & Facebook's IPO electrified the general public. &  -  &  -  & - \\ 
 %hypothesis & Facebook went public. & \checkmark   &  &  \\
 %hypothesis & General Electric went public. &  &   & \checkmark \\
 %hypothesis & People ignored Facebook's IPO. &  & \checkmark & \\

 \hline
\end{tabular}
\end{table}

However, in the real word the task can be quick challenge especially for learning algorithm. Take the following sentences are an example:  (P) Facebook's IPO electrified the general public. (H1) Facebook went public. (H2) General Electric went public. (H3) People ignored Facebook's IPO.
